Supplemental information

### 2017-10-17 manuscript/supplemental.tex
added Kate's prior-web code to SI

>>>>

      To extract the galler-parsitoid network from the same study above:

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} 
      prior\_web\_data=read.csv('tree\_level\_interaxn\_all\_plants\_traits\_size.csv')\\
      prior\_web\_data <- prior\_web\_data[,8:26]

      \# Build a web with interactions=1 for any parasitoid on any galler
      prior\_web=data.frame()

      \# each column contains all interactions for a particular parasitoid-galler combination
      for(column in 1:ncol(prior\_web\_data)){
      \hspace{-4pt}   \# the column name gives the species which makes the gall, followed by the species emerging from the gall
      \hspace{-4pt}   galler\_emerged=strsplit(colnames(prior\_web\_data)[column], "\_")
      \hspace{-4pt}   galler = galler\_emerged[[1]][1]
      \hspace{-4pt}   emerged = galler\_emerged[[1]][2]

      \hspace{-4pt}   \# the strength of the interaction is the sum of the column (number of galls across all branches sampled)
      \hspace{-4pt}   linkstrength = sum(prior\_web_data[,column])
      \hspace{-4pt}   prior\_web[as.character(galler),as.character(emerged)] <- linkstrength
      }

      \# Make the naS into 0
      prior\_web[is.na(prior\_web)] <- 0

      \# remove emerging gallers with no parasitoids
      prior\_web\_para\_only <- prior\_web[,c(2:6,8:9,12)]

      \# convert interaction strengths to 1
      prior\_web[which(prior\_web>0)] <- 1

      write.csv(prior\_web\_para\_only, file="prior\_web\_para\_only.csv", quote=F)
      }

      % # read in the data
      % prior_web_data=read.csv('../data/Salix_example/tree_level_interaxn_all_plants_traits_size.csv')
      % # just keep what we need
      % prior_web_data <- prior_web_data[,8:26]

      % # Build a web with interactions=1 for any parasitoid on any galler
      % prior_web=data.frame()

      % # each column contains all interactions for a particular parasitoid-galler combination
      % for(column in 1:ncol(prior_web_data)){
      %   # the column name gives the species which makes the gall, followed by the species emerging from the gall
      %   # they need to be separated 
      %   galler_emerged=strsplit(colnames(prior_web_data)[column], "_")
      %   galler = galler_emerged[[1]][1]
      %   emerged = galler_emerged[[1]][2]

      %   # the strength of the interaction is the sum of the column (number of galls across all branches sampled)
      %   linkstrength = sum(prior_web_data[,column])
      %   # put that into a dataframe
      %   prior_web[as.character(galler),as.character(emerged)] <- linkstrength
      % }

      % # Make the naS into 0
      % prior_web[is.na(prior_web)] <- 0
      % # Make the non-zero elements into 1
      % prior_web[prior_web>0] <- 1
      % # some of the emergers were the gallers, remove those columns if we're only
      % # interested in galler-parasitoid interactions
      % prior_web_para_only <- prior_web[,c(2:6,8:9,12)]
      % write.csv(prior_web_para_only, file="prior_web_para_only.csv", quote=F)
